Optimal Fitting of Planar Curves to Prescribed Constraints

### 2013-07-18 idp/documentation/paper.tex
started working on usability of curve design software section

	\section{Goals}

@@

>>>>

	\section{Usability of Curve Design Software}

		When trying to improve something, it seems advisable to take a step back and thoroughly research the causes of its shortcomings so as to find a way to improve it without making the same or similar mistakes. In the context of curve design tools, this can be achieved by analyzing and modelling the process that people use when designing curves. Once such a model has been obtained, it can be used to understand the issues with current tools as well as to propose criteria for good curve design tools.

@@

		\subsection{Curve Design Process}
